---
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)

land10 <- rnaturalearth::ne_download(scale = 10, type = "land", category = "physical", returnclass="sf")
rivers10 <- rnaturalearth::ne_download(scale = 10, type = "rivers_lake_centerlines", category = "physical", returnclass = "sf")
coast10 <- rnaturalearth::ne_download(scale = 10, type = 'coastline', category = 'physical', returnclass = "sf")
lakes10 <- rnaturalearth::ne_download(scale = 10, type = "lakes", category = "physical", returnclass="sf")
boundary_lines_land10 <- rnaturalearth::ne_download(scale = 10, type = 'boundary_lines_land', category = 'cultural', returnclass = "sf")

s <- data.table::fread("samples.csv", encoding = "UTF-8")

sites <- geojsonsf::geojson_sf(
  "https://raw.githubusercontent.com/dirkseidensticker/aSCAC/refs/heads/master/sites.geojson")

sites.sf <- sites

sf::st_geometry(sites) <- NULL

s.sites <- s %>%
  dplyr::left_join(
    sites,
    by = "SITE"
  ) %>%
  dplyr::distinct(
    SITE, 
    LAT, 
    LONG) %>%
  sf::st_as_sf(
    coords = c(
      "LONG", 
      "LAT"), 
    crs = 4326, 
    remove = F)

bb <- sf::st_bbox(
  s.sites)
```

# Investigating Trans-Generational Training Networks in Central Africa: A Multi-Layered Analysis of Pottery Technology (2021-2024)

This repository contains information on the above named research project at Ghent University, funded by the *Fonds voor Wetenschappelijk Onderzoek – Vlaanderen* (grant number: **1287922N**) awarded to D. Seidensticker.

```{r map, warning = FALSE, echo = FALSE, fig.align = 'center', fig.dim = c(12, 8), dpi = 300, out.width = '100%', fig.cap="Map of sampled sitese"}
ggplot() + 
  geom_sf(data = land10, fill = "white", color = NA) + 
  geom_sf(data = coast10, size = .5, color = 'darkgrey') + 
  geom_sf(data = rivers10, size = .5, color = 'darkgrey') + 
  geom_sf(data = lakes10, fill = 'darkgrey', color = NA) + 
  geom_sf(data = boundary_lines_land10, linewidth = .1, linetype = "dashed", color = 'black') + 
  geom_sf(data = s.sites) + 
  ggrepel::geom_text_repel(
    data = s.sites,
    aes(
      x = LONG,
      y = LAT,
      label = SITE
    ),
    bg.color = "white", 
    bg.r = .1,
    max.overlaps = Inf, 
    min.segment.length = 0
  ) + 
  coord_sf(
    xlim = c(
      bb[[1]], 
      bb[[3]]
    ),
    ylim = c(
      bb[[2]],
      bb[[4]]
    )
  ) + 
  ggthemes::theme_base() + 
  theme(plot.background = element_blank(), 
        axis.title = element_blank())
```


## Folder and File Structure

* `samples.csv` contains a list of all studied samples and their meta-data

## Licenses

**Figures and Tables :** [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/)
attribution requested in reuse

**Code :** [MIT License](https://opensource.org/licenses/MIT)
